R Notebook

### 2019-10-08 src/maxent_avec_xvalidation.Rmd
redoing dec issue

```{r avg asc layers cloglog}
mthna <- jul
timeslice <- jul
clogasc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^cloglog_.*.asc", full.names = TRUE)
stdep <- read.csv(paste0("../output/maxent/models/", timeslice, "/stack_depth.csv"), header = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1) #v1 corresponds to depth
  asclay$V2 <- as.character(asclay$V2) #v2 to end corresponds to year
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclay$V6 <- as.character(asclay$V6)
  asclay$V7 <- as.character(asclay$V7)
  asclay$V8 <- as.character(asclay$V8)
  asclay$V9 <- as.character(asclay$V9)
  asclay$V10 <- as.character(asclay$V10)
  asclay$V11 <- as.character(asclay$V11)
  asclay$V12 <- as.character(asclay$V12)
  asclay$V13 <- as.character(asclay$V13)
  asclay$V14 <- as.character(asclay$V14)
  asclay$V15 <- as.character(asclay$V15)

@@

  asc1998 <- raster(asclay$V2)
  asc1999 <- raster(asclay$V3)
  asc2000 <- raster(asclay$V4)
  asc2001 <- raster(asclay$V5)
  asc2002 <- raster(asclay$V6)
  asc2003 <- raster(asclay$V7)
  asc2004 <- raster(asclay$V8)
  asc2005 <- raster(asclay$V9)
  asc2006 <- raster(asclay$V10)
  asc2007 <- raster(asclay$V11)
  asc2008 <- raster(asclay$V12)
  asc2009 <- raster(asclay$V13)
  asc2010 <- raster(asclay$V14)
  asc2011 <- raster(asclay$V15)

  stkasc <- stack(asc1998, asc1999, asc2000, asc2001, asc2002, asc2003, asc2004, asc2005, asc2006, asc2007, asc2008, asc2009, asc2010, asc2011)

@@

  writeRaster(avg, paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_", asclaydep, ".asc"), overwrite=TRUE)
  avgplot <- plot(avg, png(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_", asclaydep, ".png"))) 
  dev.off()
}
```

>>>>

```{r avg asc layers cloglog}
#p <- read.csv("../output/bio/presab_nafo_yr.csv", header= TRUE)
mthna <- "nov"
mthno <- "11"
prback <- subset(p, month == mthno)
modelmonth <- cbind(paste0(mthna, unique(prback$year)))
timeslice <- modelmonth[1]

clogasc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^cloglog_.*.asc", full.names = TRUE)
stlst <- list.files(paste0("../output/maxent/models/", timeslice), pattern = "stackdepth.*.csv", full.names = TRUE)
stdep <- read.csv(stlst[1])
stdep$ascdepths <- str_sub(stdep$stackname, 9)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1) #v1 corresponds to depth
  asclay$V2 <- as.character(asclay$V2) #v2 to end corresponds to year
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclay$V6 <- as.character(asclay$V6)
  asclay$V7 <- as.character(asclay$V7)
  asclay$V8 <- as.character(asclay$V8)
  asclay$V9 <- as.character(asclay$V9)
  asclay$V10 <- as.character(asclay$V10)
  asclay$V11 <- as.character(asclay$V11)
  asclay$V12 <- as.character(asclay$V12)
  asclay$V13 <- as.character(asclay$V13)
  asclay$V14 <- as.character(asclay$V14)
  asclay$V15 <- as.character(asclay$V15)
  asclay$V16 <- as.character(asclay$V16)
  asclay$V17<- as.character(asclay$V17)
  # asclay$V18 <- as.character(asclay$V18)
  # asclay$V19<- as.character(asclay$V19)

@@

  asc1998 <- raster(asclay$V2)
  asc1999 <- raster(asclay$V3)
  asc2000 <- raster(asclay$V4)
  asc2001 <- raster(asclay$V5)
  asc2002 <- raster(asclay$V6)
  asc2003 <- raster(asclay$V7)
  asc2004 <- raster(asclay$V8)
  asc2005 <- raster(asclay$V9)
  asc2006 <- raster(asclay$V10)
  asc2007 <- raster(asclay$V11)
  asc2008 <- raster(asclay$V12)
  asc2009 <- raster(asclay$V13)
  asc2010 <- raster(asclay$V14)
  asc2011 <- raster(asclay$V15)
  asc2012 <- raster(asclay$V16)
  asc2013 <- raster(asclay$V17)
  # asc2014 <- raster(asclay$V18)
  # asc2015 <- raster(asclay$V19)

  stkasc <- stack(asc1998, asc1999, asc2000, asc2001, asc2002, asc2003, asc2004, asc2005, asc2006, asc2007, asc2008, asc2009, asc2010, asc2011, asc2012, asc2013) #, asc2014, asc2015)

@@

  writeRaster(avg, paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_", asclaydep, ".asc"), overwrite=TRUE)
  avgplot <- plot(avg, png(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_", asclaydep, ".png"))) 
  dev.off()

file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_000120.asc"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_120.asc"))
file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_000120.png"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_120.png"))
file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_041.18.asc"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_41.18.asc"))
file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_041.18.png"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_41.18.png"))
}
```

### 2019-10-08 src/plots for paper.Rmd
redoing dec issue

clogasc_list <- list.files(paste0("../output/maxent/predictions/nov"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE) #just choose a random month to calculate cells
cumst <- data.frame(0, 0)
colnames(cumst) <- c("depth", "no_cells")
for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[cum])
  ascname <- names(cumasc)
  cumst[cum, 1] <- str_sub(ascname, 13)
  cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
  ccnt <- freq(cumasc, useNA='no')
  ccnt <- sum(ccnt[ ,2])
  cumst[cum, 2] <- ccnt
}

@@

write.csv(cumst1, "../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", row.names = FALSE)

@@

first bin the probabilities for cells inside the mcp
```{r bin probabilities}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

get data to plot probability by depth... need to do manually 1-10
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec") 
binlst <- c(1:10)

@@

for (m in 1:length(mthord)){
  for (b in 1:length(binlst)){
  mth <- mthord[m]
  bin <- binlst[b]
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_binned_", bin, "_.*asc"), full.names = TRUE)

@@

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)
for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE)
  head(a)
  d <- unique(cumst1$depth)
  x <- data.frame(matrix(nrow = length(d)))
  for (s in 1:length(d)){
    dep <- d[s]
    sd <- subset(a, Depth == dep)
    sd <- subset(sd, Probability == "0 - 0.09"| Probability == "0.1 - 0.19"| Probability == "0.2 - 0.29"| Probability == "0.3 - 0.39")
    c <- sum(sd$Cells)
    x$Depth[s] <- dep
    x$Probability[s] <- "0 - 0.39"
    x$Cells[s] <- c
    x$p_cells[s] <- 1
    x$total_cells[s] <- 1
  }
  x$Cells[is.na(x$Cells)] <- 0
   for (r in 1:nrow(x)){
     d1 <- str_sub(x$Depth[r], end = 4)
     for (ro in 1:nrow(cumst1)){
       d2 <- str_sub(cumst1$depth[ro], end = 4)
       if (d1 == d2){
           x$total_cells[r] <- cumst1$no_cells[ro]
       }
     }
   }
  for (r in 1:nrow(x)){
    x$p_cells[r] <- (x$Cells[r]/x$total_cells[r])*100
  }
x <- subset(x, select = -c(matrix.nrow...length.d..))
  write.csv(x, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"))
}
```

@@

>>>>

clogasc_list <- list.files(paste0("../output/maxent/predictions/dec"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE) #just choose a random month to calculate cells
cumst <- data.frame(0, 0)
colnames(cumst) <- c("depth", "no_cells")
for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[6])
  ascname <- names(cumasc)
  cumst[cum, 1] <- str_sub(ascname, 13)
  cumasc2 <- raster::mask(cumasc, outsidemcp, inverse = TRUE)
  ccnt <- freq(cumasc2, useNA='no')
  ccnt <- sum(ccnt[ ,2])
  cumst[cum, 2] <- ccnt
}

@@

write.csv(cumst1, "../output/maxent/paper_plots/prob_by_depth/cellsperlayermar.csv", row.names = FALSE)

@@

first bin the probabilities for cells inside the mcp

XXXXFROM HERE XXXXX
```{r bin probabilities}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

get data to plot probability by depth... 
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
binlst <- c(1:10)

@@

for (m in 1:length(mthord)){
  for (b in 1:length(binlst)){
  mth <- mthord[m]
  bin <- binlst[b]
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_binned_", bin, ".*asc"), full.names = TRUE)

@@

```{r}
mthord <- c("dec") #"mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", 
cumst1 <- read.csv("../output/maxent/paper_plots/prob_by_depth/cellsperlayer.csv", header = TRUE)
for (m in 1:length(mthord)){
  mth <- "dec" #mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_dis_prob_cells.csv"), header = TRUE)
  head(a)
  d <- unique(cumst1$depth)
  x <- data.frame(matrix(nrow = length(d)))
  for (s in 1:length(d)){
    dep <- d[s]
    sd <- subset(a, Depth == dep)
    sd <- subset(sd, Probability == "0 - 0.09"| Probability == "0.1 - 0.19"| Probability == "0.2 - 0.29"| Probability == "0.3 - 0.39")
    c <- sum(sd$Cells)
    x$Depth[s] <- dep
    x$Probability[s] <- "0 - 0.39"
    x$Cells[s] <- c
    x$p_cells[s] <- 1
    x$total_cells[s] <- 1
  }
  x$Cells[is.na(x$Cells)] <- 0
   for (r in 1:nrow(x)){
     d1 <- str_sub(x$Depth[r], end = 4)
     for (ro in 1:nrow(cumst1)){
       d2 <- str_sub(cumst1$depth[ro], end = 4)
       if (d1 == d2){
           x$total_cells[r] <- cumst1$no_cells[ro]
       }
     }
   }
  for (r in 1:nrow(x)){
    x$p_cells[r] <- (x$Cells[r]/x$total_cells[r])*100
  }
x <- subset(x, select = -c(matrix.nrow...length.d..))
  write.csv(x, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_u0.4plus_dis_prob_cells.csv"))
}
```

@@

```{r}
mar <- read.csv("../output//maxent/paper_plots/prob_by_depth/mar_u0.4s_dis_prob_cells.csv", header = TRUE)
mar$Probability <- gsub(">0.9", "0.9 - 1", mar$Probability)
mar$Depth <- as.factor(mar$Depth)
flevelsm <- levels(mar$Depth)
flevelsm <- rev(flevelsm)

jun <- read.csv("../output//maxent/paper_plots/prob_by_depth/jun_u0.4s_dis_prob_cells.csv", header = TRUE)
jun$Probability <- gsub(">0.9", "0.9 - 1", jun$Probability)
jun$Depth <- as.factor(jun$Depth)
flevelsj <- levels(jun$Depth)
flevelsj <- rev(flevelsj)

sep <- read.csv("../output//maxent/paper_plots/prob_by_depth/sep_u0.4s_dis_prob_cells.csv", header = TRUE)
sep$Probability <- gsub(">0.9", "0.9 - 1", sep$Probability)
sep$Depth <- as.factor(sep$Depth)
flevelss <- levels(sep$Depth)
flevelss <- rev(flevelss)

dec <- read.csv("../output//maxent/paper_plots/prob_by_depth/dec_u0.4s_dis_prob_cells.csv", header = TRUE)
dec$Probability <- gsub(">0.9", "0.9 - 1", dec$Probability)
dec$Depth <- as.factor(dec$Depth)
flevelsd <- levels(dec$Depth)
flevelsd <- rev(flevelsd)

probcol <- rev(brewer.pal(7,"RdYlGn"))

ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsm, breaks=flevelsm[seq(1,length(flevelsm), by = 2)]) + coord_flip()

ggplot(jun, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsj, breaks=flevelsj[seq(1,length(flevelsj), by = 2)]) + coord_flip()

ggplot(sep, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelss, breaks=flevelss[seq(1,length(flevelss), by = 2)]) + coord_flip()

ggplot(dec, aes(Depth, p_cells, fill = Probability)) + geom_col() + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsd, breaks=flevelsd[seq(1,length(flevelsd), by = 2)]) + coord_flip()
```

### 2019-10-08 src/testing_file.Rmd
redoing dec issue

>>>>

#argh
```{r}
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

clogasc_list <- list.files(paste0("../output/maxent/predictions/dec"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE) #just choose a random month to calculate cells
cumst <- data.frame(0, 0)
colnames(cumst) <- c("depth", "no_cells")
for (cum in 1:length(clogasc_list)){
  cumasc <- raster(clogasc_list[6])
  ascname <- names(cumasc)
  cumst[cum, 1] <- str_sub(ascname, 13)
  cumasc2 <- raster::mask(cumasc, outsidemcp, inverse = TRUE)
  ccnt <- freq(cumasc2, useNA='no')
  ccnt <- sum(ccnt[ ,2])
  cumst[cum, 2] <- ccnt
}

clogasc_listm <- list.files(paste0("../output/maxent/predictions/mar"), pattern = "^avg_cloglog_.*.asc", full.names = TRUE) #just choose a random month to calculate cells
cumstm <- data.frame(0, 0)
colnames(cumstm) <- c("depth", "no_cells")
for (cum in 1:length(clogasc_listm)){
  cumascm <- raster(clogasc_listm[6])
  ascnamem <- names(cumascm)
  cumstm[cum, 1] <- str_sub(ascnamem, 13)
  cumasc2m <- raster::mask(cumascm, outsidemcp, inverse = TRUE)
  ccntm <- freq(cumasc2, useNA='no')
  ccntm <- sum(ccntm[ ,2])
  cumstm[cum, 2] <- ccntm
}

write.csv(cumst1, "../output/maxent/paper_plots/prob_by_depth/cellsperlayermar.csv", row.names = FALSE)

```{r avg asc layers cloglog xx}
#p <- read.csv("../output/bio/presab_nafo_yr.csv", header= TRUE)
mthna <- "nov"
mthno <- "11"
prback <- subset(p, month == mthno)
modelmonth <- cbind(paste0(mthna, unique(prback$year)))
timeslice <- modelmonth[1]

clogasc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^cloglog_.*.asc", full.names = TRUE)
stlst <- list.files(paste0("../output/maxent/models/", timeslice), pattern = "stackdepth.*.csv", full.names = TRUE)
stdep <- read.csv(stlst[1])
stdep$ascdepths <- str_sub(stdep$stackname, 9)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1) #v1 corresponds to depth
  asclay$V2 <- as.character(asclay$V2) #v2 to end corresponds to year
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclay$V6 <- as.character(asclay$V6)
  asclay$V7 <- as.character(asclay$V7)
  asclay$V8 <- as.character(asclay$V8)
  asclay$V9 <- as.character(asclay$V9)
  asclay$V10 <- as.character(asclay$V10)
  asclay$V11 <- as.character(asclay$V11)
  asclay$V12 <- as.character(asclay$V12)
  asclay$V13 <- as.character(asclay$V13)
  asclay$V14 <- as.character(asclay$V14)
  asclay$V15 <- as.character(asclay$V15)
  asclay$V16 <- as.character(asclay$V16)
  asclay$V17<- as.character(asclay$V17)
  # asclay$V18 <- as.character(asclay$V18)
  # asclay$V19<- as.character(asclay$V19)

  asc1998 <- raster(asclay$V2)
  asc1999 <- raster(asclay$V3)
  asc2000 <- raster(asclay$V4)
  asc2001 <- raster(asclay$V5)
  asc2002 <- raster(asclay$V6)
  asc2003 <- raster(asclay$V7)
  asc2004 <- raster(asclay$V8)
  asc2005 <- raster(asclay$V9)
  asc2006 <- raster(asclay$V10)
  asc2007 <- raster(asclay$V11)
  asc2008 <- raster(asclay$V12)
  asc2009 <- raster(asclay$V13)
  asc2010 <- raster(asclay$V14)
  asc2011 <- raster(asclay$V15)
  asc2012 <- raster(asclay$V16)
  asc2013 <- raster(asclay$V17)
  # asc2014 <- raster(asclay$V18)
  # asc2015 <- raster(asclay$V19)

  stkasc <- stack(asc1998, asc1999, asc2000, asc2001, asc2002, asc2003, asc2004, asc2005, asc2006, asc2007, asc2008, asc2009, asc2010, asc2011, asc2012, asc2013) #, asc2014, asc2015)

file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_000120.asc"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_120.asc"))
file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_000120.png"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_120.png"))
file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_041.18.asc"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_41.18.asc"))
file.rename(paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_041.18.png"), paste0("../output/maxent/predictions/", mthna, "/avg_cloglog_41.18.png"))
}
